---
author: "Tsu-Hao, Yu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part I. Basic R Syntax (30 points)

#### Question 1. Hello World! (5 points)

Here's an R code chunk that prints the text 'Hello world!'.

```{r}
print("Hello world!")
```

#### Modify the code chunk below to print your name

```{r}
print("Tsu-Hao, Yu")
```

<br>

#### Question 2. Play with Dataset (25 points)

The following is a small data to store health information, where the unit for height is centimeters and weight is kilogram.

```{r}
BMI = data.frame(
   gender = c("Male", "Male","Female"), 
   height = c(152, 171.5, 165), 
   weight = c(81,93,78),
   Age = c(42,38,26)
)
print(BMI)
```

#### a) Please calculate BMI for each person and add that information to the dataframe and display the new dataframe. (10 points)

**BMI Formula: Weight (kg)/Square of Height(meters)**

```{r}
BMI$bmi = BMI$weight / (BMI$height / 100)^2
print(BMI)
```

#### b) Please display `gender` and `age` for the people with BMI great than 30. (10 points)

```{r}
print(BMI[BMI$bmi > 30, c("gender", "Age")])
```

#### c) Please display `gender` for the people with BMI great than 25 and age less than 30. (5 points)

```{r}
BMI[BMI$bmi > 25 & BMI$Age > 30, c("gender")]
```
