---
author: "Tsu-Hao, Yu"
date: "Due Date 2/17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part I. Changing the author field and file name.

#### (a) Change the `author:` field on the Rmd document 

#### (b) Rename this file to "HW1_YourFirstInitialYourLastName.Rmd", (e.g. HW1_YDing.Rmd).

<br>


### Part II. Cars data (44 points)

We'll look at data frame and plotting in much more detail in later classes.  For a previous of what's to come, here's a very basic example.

For this example we'll use a very simple dataset.  The `cars` data comes with the default installation of R.  To see the first few rows of the data, just type `head(cars)`.

```{r}
head(cars)
```

#### (a) Do a summary for `cars`. What the min,max, mean and median values of `speed` and `dist`? (5 points)

```{r}
summary(cars)
```

> cars.speed
<br>
min:4.0
<br>
max:25.0
<br>
mean:15.4
<br>
median:15.0

>cars.dist
<br>
min:2.0
<br>
max:120.0
<br>
mean:42.98
<br>
median:36.0

#### (b) Calculate the variance and standard deviation of `speed` (5 points)

```{r}
var(cars$speed)
sd(cars$speed)
```

> var:27.95918
<br>
sd:5.287644


#### (c) Calculate the variance and standard deviation of `dist` (5 points)

```{r}
var(cars$dist)
sd(cars$dist)
```

> var:664.0608
<br>
sd:25.76938

#### (d) Calulate the average and standard deviation of `dist` when `speed`  is greater than 12 and less than 19. (5 points)

```{r}
dist_data <- subset(cars, speed > 12 & speed < 19)
mean(dist_data$dist)
sd(dist_data$dist)
```

> mean:44.7
<br>
sd:18.61833


#### (e) Produce a histogram of `speed` with **10 bins**. Please illustrate your observation from the output. (6 points)

```{r}
hist(cars$speed, breaks = seq(4,25,l=11), main = "Histogram of Speed", xlab = "Speed", col = "blue")
```

> According to the histogram, Most car speed were around 10-20, and the car of speed 4-10 and 20-25 took pretty much the same amount.

#### (f) Produce a histogram of `dist` with **20 bins**. Please illustrate your observation from the output. (6 points)

```{r}
hist(cars$dist, breaks = seq(2,120,l=21), main = "Histogram of Distance", xlab = "Distance", col = "green")
```

> According to the histogram, Most driver drove about 20-60, and then 60-120, the shortest distance were 0-20.

#### (g) Use the `boxplot` function to create a boxplot of `speed`. Please illustrate your observation from the output. (6 points)

```{r}
boxplot(cars$speed, col = "lightblue")
abline(h = min(cars$speed), col = "Blue")
abline(h = max(cars$speed), col = "Yellow")
abline(h = median(cars$speed), col = "Green")
abline(h = quantile(cars$speed, c(0.25, 0.75)), col = "Red")
```

> The boxplot shows that the min is below 5, max is 25 and median is 15, there were no outliers exist.

#### (h) Use the `boxplot` function to create a boxplot of `dist`. Please illustrate your observation from the output. (6 points)

```{r}
boxplot(cars$dist, col = "lightgreen")
abline(h = min(cars$dist), col = "Blue")
abline(h = max(cars$dist), col = "Yellow")
abline(h = median(cars$dist), col = "Green")
abline(h = quantile(cars$dist, c(0.25, 0.75)), col = "Red")
```

> The boxplot shows that the min is just above 0, max is 120 and median is 40, there were outliers exist.

<br>

### Part III. Random Variables (26 points)

#### Question 1. Classify the following random variables as discrete or continuous (12 points):

X: the number of automobile accidents per year in Illinois.

> Discrete

Y: the length of time to play 18 holes of golf.

> Continuous

M: the amount of milk produced yearly by a particular cow.

> Continuous

N: the number of eggs laid each month by a hen.

> Discrete

P: the number of building permits issued each month in a certain city.

> Discrete

Q: the weight of grain produced per acre.

> Continuous

#### Question 2: Multiple Choices (14 points):

#### i) A discrete random variable

A) Takes on only countable values

B) Takes on any value in an interval

C) Has a probability density function

> A

#### ii) A continuous random variable is different from a discrete random variable because:

A) It can only take integer values

B) It is described using a probability mass function (PMF)

C) It can take an infinite number of values within a given range

> C

#### iii) If $X$ is a constant random variable, meaning $X=c$ for some constant $c$, what is $Var(X)$? 

A) 0

B) $c^2$

C) $E[X]$

D) $E[X^2]$

> A

#### iv) Which of the following statements about expectation is TRUE?

A) $E[X]$ is always equal to the sample mean

B) $E[X]$ can be estimated by the sample mean when the sample size is large
	
C) $E[X]$ is always equal to the variance of X

D) $E[X]$ is always an integer

> B

#### v) What does a histogram represent?

A) The distribution of a single variable
	
B) The cumulative frequency of data

C) The median and quartiles of data

> A

#### vi) If a histogram is skewed to the right, what does it indicate? 

A) The mean is greater than the median

B) The median is greater than the mean

C) The data is symmetric

D) The data has no outliers

> A

#### vii) Which of the following is true about outliers in a boxplot?

A) Outliers are always errors in the data

B) Outliers are represented by dots or asterisks outside the whiskers
	
C) Outliers are included in the box

D) Outliers are not shown in a boxplot

> B

### Part IV. Normal Distributions and Critial Values (30 points)

#### Question 1: A soft-drink machine is regulated so that it discharges an average of 200 milliliters per cup. If the amount of drink is normally distributed with a standard deviation equal to 15 milliliters,

#### (a) what fraction of the cups will contain more than 224 milliliters?  (5 points)

**Hint**: You can use `pnorm` or `pnormGC`(need `tigerstats` packagee).

```{r}
# pnorm can give us the rate >= 224
1 - pnorm(224, mean = 200, sd = 15)
```

#### (b) what is the probability that a cup contains between 191 and 209 milliliters? (5 points)

```{r}
pnorm(209, mean = 200, sd = 15) - pnorm(191, mean = 200, sd = 15)
```

#### (c) below what value do we get the smallest 25% of the drinks? (5 points)

```{r}
qnorm(0.25, mean = 200, sd = 15)
```


#### Question 2. Critical values with `qnorm` 

#### (a) Please use `qnorm` to find the critical values $z_{0.025}$. (5 points)

```{r}
qnorm(0.975)
```

#### (b) Please use `qnorm` to find the critical values $z_{0.005}$. (5 points)

```{r}
qnorm(0.995)
```

#### (c) Which value is larger? Why? (5 points)

> Type your answer here
z_{0.005} is larger because it corresponds to a higher cumulative probability
