---
title: "In Class Exercise 4"
author: "Tsu-Hao, Yu"
date: "2025-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### In-class Exercise: `geom_bar()`

Please use `barplot` and `geom_bar()` to investigate `clarity` attribute in `diamonds` data set.

```{r}
library(ggplot2)
barplot(table(diamonds$clarity)) #regular way
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = clarity))
```


#### In-class Exercise: Investigate Two Categorical Variables

1. Please use `geom_bar()` to investigate the relationship between `clarity` and `cut`.

```{r}
ggplot(data = diamonds, aes(x = clarity)) +
  geom_bar(aes(fill = cut)) 
ggplot(data = diamonds, aes(x = clarity)) +
  geom_bar(aes(fill = cut), position = "fill")  #normalized the barplot
ggplot(data = diamonds, aes(x = clarity)) +
  geom_bar(aes(fill = cut), position = "fill") +
   coord_flip() #normalized the barplot and make it horizontal
```


2. Please use `geom_count()` to investigate the relationship between `clarity` and `cut`.

```{r}
ggplot(data = diamonds) +
  geom_count(mapping = aes(x = clarity, y = cut))
```

#### In-class Exercise: Investigate A Categorical and A Continuous Variable by `geom_histogram()`

1. Please use `geom_histogram()` to investigate the relationship between `price` and `color`.

```{r}
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(aes(fill = color), bins = 30, color = "black")  #have black lines around each bar
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(aes(fill = color), bins = 30, color = "black", position = "fill") 
```


2. Please use `geom_histogram()` to investigate the relationship between `price` and `clarity`.


```{r}
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(aes(fill = clarity), bins = 30, color = "black")  #have black lines around each bar
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(aes(fill = clarity), bins = 30, color = "black", position = "fill") 
```

3. Please use `geom_histogram()` to investigate the relationship between `Sepal.Length` and `Species` in `iris` data set.

```{r}
ggplot(data = iris, aes(x = Sepal.Length)) +
  geom_histogram(aes(fill = Species), bins = 20, color = "black")  #have black lines around each bar
ggplot(data = iris, aes(x = Sepal.Length)) +
  geom_histogram(aes(fill = Species), bins = 20, color = "black", position = "fill") 
```



4. Please use `geom_histogram()` to investigate the relationship between `Petal.Length` and `Species` in `iris` data set.

```{r}
ggplot(data = iris, aes(x = Petal.Length)) +
  geom_histogram(aes(fill = Species), bins = 20, color = "black")  #have black lines around each bar
ggplot(data = iris, aes(x = Petal.Length)) +
  geom_histogram(aes(fill = Species), bins = 20, color = "black", position = "fill") 
```


#### In-class Exercise: Investigate A Categorical and A Continuous Variable by `geom_boxplot`

1. Please use `geom_boxplot()` to investigate the relationship between `price` and `color`. You can choose to flip the boxplot or not.

```{r boxplotdiamond}
ggplot(data = diamonds) +
  geom_boxplot( mapping = aes(x = color, y = price))
ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = reorder(color, price, FUN = median), y = price))
```

2. Please use `geom_boxplot()` to investigate the relationship between `Sepal.Length` and `Species` in the `iris` data set. You can choose to flip the boxplot or not.

```{r boxplotiris}
ggplot(data = iris) +
  geom_boxplot( mapping = aes(x = Species, y = Sepal.Length))
ggplot(data = iris) +
  geom_boxplot( mapping = aes(x = Species, y = Petal.Length))

```

#### In-class Exercise: Two Continuous Variables by `geom_point()`

1. Please use `geom_point()` to investigate the relationship between `depth` and `price`.

```{r}
ggplot(data = diamonds) +
  geom_point(mapping = aes(x = depth, y = price))
```


2. Please use `geom_point()` to investigate the relationship between `Petal.Length` and `Petal.Width` with `Species` in `iris` dataset.

```{r irispoint}
ggplot(data = iris) +
  geom_point(mapping = aes(x = Petal.Length, y = Petal.Width,colour = Species))

```

#### In-class Exercise: Two Continuous Variables by `geom_boxplot()`
1. Please use `geom_boxplot()` to investigate the relationship between `depth` and `price`. How to choose the width?

```{r}
ggplot(data = diamonds, mapping = aes(x = depth, y = price)) +
  geom_boxplot(mapping = aes(group = cut_width(depth, 0.5)))
ggplot(data = diamonds, mapping = aes(x = price, y = depth)) +
  geom_boxplot(mapping = aes(group = cut_width(price, 500)))
```


2. Please use `geom_boxplot()` to investigate the relationship between `Sepal.Length` and `Sepal.Width`. How to choose the width?

```{r}
ggplot(data = iris, mapping = aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_boxplot(mapping = aes(group = cut_width(Sepal.Length, 0.2)))
```

