---
title: "In Class Exercise 6"
author: "Tsu-Hao, Yu"
date: "2025-02-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### In-class Exercise: CI on mean

A manufacturer of sports equipment has developed a new synthetic fishing line with a standard
deviation of 0.5 kilogram. If a random sample of 50 lines is tested and found
to have a mean breaking strength of 7.8 kilograms, can you construct a $99\%$ confidence interval.

Here
\[\sigma = 0.5, \qquad n = 50, \qquad \bar{x} = 7.8, \qquad \alpha = 0.01.\]

```{r}
n <- 50 #sample size
xbar <- 7.8  #sample mean
sigma <- 0.5  #population sd
alpha <- 0.01
#Left endpoint for confidence 99%
lend <- xbar - sigma/sqrt(n)*qnorm(1-alpha/2)
#Right endpoint for confidence 99%
rend <- xbar + sigma/sqrt(n)*qnorm(1-alpha/2)
```

The $99\%$ confidence interval is (`r lend`, `r rend`). 

#### In-class Exercise: CI on $\mu$ with unknown variance

1. Regular consumption of presweetened cereals contributes to tooth decay, heart disease,
and other degenerative diseases, according to studies conducted by Dr. W. H. Bowen
of the National Institute of Health and Dr. J. Yudben, Professor of Nutrition and
Dietetics at the University of London. In a random sample consisting of 20 similar
single servings of Alpha-Bits, the average sugar content was 11.3 grams with a standard
deviation of 2.45 grams. Assuming that the sugar contents are normally distributed,
construct a 95% confidence interval for the mean sugar content for single servings of
Alpha-Bits.

Here
\[n = 20, \qquad \bar{x} = 11.3, \qquad s = 2.45, \qquad \alpha = 0.05.\]



```{r}
xbar <- 11.3
s <-2.45
n <- 20
alpha <- 0.05
tcritical<- qt(1-alpha/2,n-1)
lowerBound <- xbar-tcritical*s/sqrt(n)
lowerBound
upperBound <- xbar+tcritical*s/sqrt(n)
upperBound
```


2. Please construct a 95% confidence interval for the mean of `Sepal.Length` in the `iris` data set, assume the normal distribution.

Method I:

```{r}
sepalLength<- iris$Sepal.Length
xbar <- mean(sepalLength)
s <-sd(sepalLength)
n <- length(sepalLength)
alpha <- 0.05
tcritical<- qt(1-alpha/2,n-1)
lowerBound <- xbar-tcritical*s/sqrt(n)
lowerBound
upperBound <- xbar+tcritical*s/sqrt(n)
upperBound
```

t-test

```{r}
t.test(sepalLength)
```

#### In-class Exercise: CI on $\mu_1-\mu_2$ with known $\sigma_1$ and $\sigma_2$

1. Generate 50 normal random numbers with $\mu_1 = 3$ and $\sigma_1 = 3$ and get the sample mean $\bar{x}_1$.
Hint: `rnorm`

```{r}
n1<-50
x1<-rnorm(n1,mean = 3,sd = 3)
x1bar<-mean(x1)
x1bar
```


2. Generate 75 normal random numbers with $\mu_2 = 2$ and $\sigma_2 = 4$ and get the sample mean $\bar{x}_2$

```{r}
n2<-75
x2<-rnorm(n2,mean = 2,sd = 4)
x2bar<-mean(x2)
x2bar
```


3. Please construct a 95% confidence interval on $\mu_1-\mu_2$.

```{r}
alpha<-0.05
sigma1 <- 2
sigma2 <- 4
standerror <- sqrt(sigma1^2 /n1 + sigma2^2/n2)
lowerBound <- x1bar-x2bar - qnorm(1-alpha/2)*standerror
lowerBound
upperBound <- x1bar-x2bar + qnorm(1-alpha/2)*standerror
upperBound
```



#### In-class Exercise A: CI on $\mu_1-\mu_2$ with unknown $\sigma_1 = \sigma_2$

Let's play with `iris` data set. We want to compare the population mean of `Sepal.Length` between `Setosa` and `Virginica`. Suppose we know these two species come from the normal distribution with the same variance. Can you construct a confidence interval on $\mu_{virginica}-\mu_{setosa}$ with 95% confidence?

```{r}
irisTwoSpeices<-subset(iris,Species %in% c("virginica", "setosa"))
t.test(Sepal.Length~Species,data = irisTwoSpeices,var.equal = TRUE)
setosaSepal<-iris$Sepal.Length[iris$Species == "setosa"]
virginicaSepal<-iris$Sepal.Length[iris$Species == "virginica"]
t.test(virginicaSepal,setosaSepal,var.equal = TRUE)
```


#### In-class Exercise B: CI on $\mu_1-\mu_2$ with unknown $\sigma_1 \ne \sigma_2$

Let's play with `iris` data set. We want to compare the population mean of `Sepal.Length` between `Setosa` and `Virginica`. Suppose we know these two species come from the normal distribution with different variances. Can you construct a confidence interval on $\mu_{virginica}-\mu_{setosa}$ with 95% confidence?

```{r}
t.test(Sepal.Length~Species,data = irisTwoSpeices)
t.test(virginicaSepal,setosaSepal,var.equal = TRUE)
```


