---
title: "In Class Exercise 3"
author: "Tsu-Hao, Yu"
date: "2025-02-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### In-class Exercise: Normal Distribution
1. Suppose $X \sim \mathcal{N}(-1,3^2)$, please generate the random numbers with sample size $n = 1e6$.

```{r}
n <- 1e6 # number of sample size
x <- rnorm(n, mean = -1, sd = 3) # generate the standard normal random numbers
```


2. Do a histogram for the instances you generated with the y-axis as relative frequency instead of frequency.

```{r}
hist(x,probability=TRUE,main="normal random numbers with mean= -1 and sd =3") # histogram of the relative frequency
```


3. Find Q1, sample median, Q3, sample mean, and sample variance of the sample you generated. Compare your results with the mean and variance of the random variable. 

```{r}
summary(x)
var(x)
qnorm(0.25, mean = -1, sd = 3) # find Q1 of the random variable Z
qnorm(0.75, mean = -1, sd = 3)
```

#### In-class Exercise: *pnormGC*

```{r, message=FALSE}
library(tigerstats) #import needed package
```

The midterm exam scores in ITMD/ITMS/STAT 514 are normally distributed with mean 85 and standard deviation 8. Please use *pnormGC* to find the following:

a. What fraction of the scores lies between 80 and 90? 

```{r}
pnormGC(c(80,90),mean = 85, sd = 8, region = "between",graph = TRUE) 
#just reference to show outside
pnormGC(c(80,90),mean = 85, sd = 8, region = "outside",graph = TRUE) 
```


b. What fraction of the scores lies above 90?

```{r}
pnormGC(90,mean = 85, sd = 8, region = "above",graph = TRUE) 
1-pnorm(90,mean = 85,sd = 8)
```


c. What fraction of the scores lies below 80?

```{r}
pnormGC(80,mean = 85, sd = 8, region = "below",graph = TRUE) 
pnorm(80,mean =85,sd = 8)
```


#### In-class Exercise: Critical Values

1. Find the value of $z_0$ such that $99\%$ of the standard normal $Z$ values lie between $-z_0$ and $z_0$; that is, $P(-z_0\leq Z\leq z_0) = .99$.

**Answer**:	\[P(-z_0\le Z \le z_0) 
 = 1- 2P(Z <-z_0) = 0.99 \Rightarrow P(Z<-z_0) = 1-P(Z<z_0) = 0.005.\]

```{r}
-qnorm(0.005)
qnorm(1-0.005)
```


2. Find $z_\alpha$ when $\alpha = 0.01$.

```{r}
alpha<- 0.01
zalpha <- qnorm(1-alpha)
zalpha

```


#### In-class Exercise: Play with QQ-plot

Please use the above plot to investigate `medv` in the data set `Boston` built in `MASS` package.

```{r, message=FALSE}
# Please use the following code to access the data set Boston 
library(MASS)# Need MASS package
data(Boston)
summary(Boston)
```

- *qqPlot*


```{r}
library(car)
qqPlot(Boston$medv)
```


- *qqnorm*

```{r}
qqnorm(Boston$medv, pch = 3)
qqline(Boston$medv, col = "purple")
```

- *qplot*

```{r}
library(ggplot2)
ggplot(Boston,aes(sample=medv))+stat_qq()
qplot(sample = medv, data = Boston)
```

